Manuscript 1 code

### 2024-09-11 manuscript_1_code.Rmd
NAK incorporated discussion from 9/11 AM on functional group classification

```{r cover plot setup}
cover_df <- data.frame(
  year = data$year,
  habitat = data$habitat,
  site = data$site,
  location = data$location,
  coral = data$coral,
  cca = data$crustose_corallines + data$lithophyllum_kotschyanum + data$neogoniolithon_brassica_florida + data$sporolithon_sp,
  macroalgae = rowSums(macro_species_cols),
  turf = data$coral_rubble + data$algal_turf + data$bare_space + data$damselfish_turf + data$cyanophyta,
  sand = data$sand,
  other = data$ascidian + data$corallimorpharia + data$heteractis_sp + data$millepora_platyphylla + data$sarcophyton_sp + data$shell_debris +
    data$soft_coral + data$sponge + data$tridacna_sp + data$zooxanthellae + data$no_data
)

@@

#ggsave(filename = "output/figure_1.png", figure_1, height = 10, width = 14)
```

>>>>

```{r cover plot setup}
cover_df <- data.frame(
  year = data$year,
  habitat = data$habitat,
  site = data$site,
  location = data$location,
  coral = data$coral,
  cca = data$crustose_corallines + data$lithophyllum_kotschyanum + data$neogoniolithon_brassica_florida + data$sporolithon_sp,
  macroalgae = rowSums(macro_species_cols),
  turf = data$algal_turf  + data$damselfish_turf, 
  sand = data$sand,
  coral_rubble = data$coral_rubble,
  cyanophyta = data$cyanophyta,
  other = data$ascidian + data$corallimorpharia + data$heteractis_sp + data$millepora_platyphylla + data$sarcophyton_sp + data$shell_debris +
    data$soft_coral + data$sponge + data$tridacna_sp + data$zooxanthellae + data$no_data + data$bare_space
)

@@

ggsave(filename = "output/figure_1.png", figure_1, height = 10, width = 14)
```
